A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-22 6_validation.tex
move computation time to results

\paragraph{Accuracy}
In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get strange artifacts at corners in the toolpath.
We therefore use a semi-circle with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position.
In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
See \cref{segment_visualization}.

@@

\paragraph{Uniformity}
Depending on the printer hardware configuration, some bead widths might be difficult or impossible to manufacture.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
Also, large bead widths can cause the extruded material to bulge upwards instead of filling the required width.
\todo{Include picture of flutter?}
Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.

>>>>

\paragraph{Computation time}
The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
The number of elements in the trapezoidation is linear in the number of elements in the VD
and all of the stages of our framework are also linear in the number of elements in the skeleton,
so the total running time of our algorithm is $O(n \log n)$.

From the experimental results shows in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $10^{-5} n \log n$ seconds.
The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.

% only Moessen reports on computation times, but in a weird manner

\subsubsection{Accuracy}
In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get strange artifacts at corners in the toolpath.
We therefore use a semi-circle with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position.
In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
See \cref{segment_visualization}.

@@

\subsubsection{Uniformity}
Depending on the printer hardware configuration, some bead widths might be difficult or impossible to manufacture.
A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
Also, large bead widths can cause the extruded material to bulge upwards instead of filling the required width.
\todo{Include picture of flutter?}
Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.
